Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-02 main_revision.tex

The time-dependence of the responses generates an interesting issue for interpretation. The first year responses are illustrative of the short-term immediate impacts of change, whereas the longer-term responses are heavily dominated by the feedback responses. Further, depiction of absolute vs. relative differences can serve to highlight different aspects of the model response. Here we report values from 15-20 years after fertilization began, to be consistent with the methodology used by \cite{wieder2019} in their analysis of global fertilization of the default model, and to capture the dynamics of the whole system feedbacks captured in Fig. \ref{timescales}.  Thus, figures \ref{GPP_CN} and \ref{LAI_CN} illustrate the responses to 15-20 years of CO$_{2}$ and N  fertilization simultaneously, for GPP and LAI. Corresponding figures for NPP, vegetation carbon and $N_{area}$ are in the supplemental information (SI Figures 1-3). Figures for each site showing the individual N and CO$_{2}$ responses are also included in the SI (Figures 3 to 10).

\subsubsection{Impact of parameters}
 the parameter response space of the model is complex with regard to these changing initial conditions, environments, and drivers on global change. Again, we go through the parameters one at a time to highlight the primary features of the model response and how they relate to expectations based on model structure.

The strong impact of \emph{slatop} had important implications for the initial state in many cases, and for several of the lower values, we screened out the results of the fertilization on account of very low LAIs (which resulted in erratic fertilization responses). The impact of \emph{slatop} on fertilization was different at every site. For example, at Metolius, high  \emph{slatop} was related to high N responses, plausibly since these cheaper leaves could produce a greater LAI/GPP feedback in response to the N fertilization. At Niwot Ridge, high SLA was related to strong GPP responses to CO$_{2}$. These simulations have higher water limitation (on account of their larger canopies, figure \ref{btran state}) and so respond more vigarously to the increased water use efficiency of high CO$_{2}$ growth conditions (while reducing their NPP and LAI with N fertilization, on account of higher respiration costs). These contrasting results are illustrative of the complexity of the interactions between model initial state, environmental forcing and parameterization, and of the need to understand how multiple simultaneous growth limitations can influence responses to climate forcing.

@@

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parameteric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on gross primary productivity (GPP). }
     \label{GPP_CN}
  \end{figure}

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on net primary productivity (NPP).}
     \label{NPP_CN}
  \end{figure}

  \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_relCNdep_defpft_TLAI_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on leaf area index (LAI).}
     \label{LAI_CN}
  \end{figure}

>>>>

The time-dependence of the responses generates an interesting issue for interpretation. The first year responses are illustrative of the short-term immediate impacts of change, whereas the longer-term responses are heavily dominated by the feedback responses. Further, depiction of absolute vs. relative differences can serve to highlight different aspects of the model response. Here we report values from 15-20 years after fertilization began, to be consistent with the methodology used by \cite{wieder2019} in their analysis of global fertilization of the default model, and to capture the dynamics of the whole system feedbacks captured in Fig. \ref{timescales}.  Thus, figures \ref{GPP_CN} and \ref{LAI_CN} illustrate the responses to 15-20 years of CO$_{2}$ and N  fertilization simultaneously, for GPP and LAI.  Note that each figure is a different scale to best illustrate the parametric impacts.  Corresponding figures for NPP, vegetation carbon and $N_{area}$ are in the supplemental information (SI Figures 1-3). Figures for each site showing the individual N and CO$_{2}$ responses are also included in the SI (Figures 3 to 10).

\subsubsection{Impact of parameters}
The parameter response space of the model is complex, and parameter impacts on fertilization responses vary with changing initial conditions and with treatment. Here, we discuss the major impacts of each parameter on the responses and how they relate to expectations based on model structure.

The impact of \emph{slatop} on fertilization was different at every site. For MET, \emph{slatop} was the most important control over N responses, with cheaper leaves allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found.

@@

 \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_at_relCNdep_defpft_GPP_y2013.png}
     \caption{Influence of parameteric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on gross primary productivity (GPP). }
     \label{GPP_CN}
  \end{figure}

  \begin{figure}[h]
     \includegraphics[width=1.35\textwidth]{matlab/figures/MAY19jp_at_relCNdep_defpft_TLAI_y2013.png}
     \caption{Influence of parametric variation on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5Kg/m$^{-2}$/y N fertilization on leaf area index (LAI). Note changes in scale between plots to show detail.}
     \label{LAI_CN}
  \end{figure}
